---
title: "Teaching"
---

I am **on sabbatical** for the 2023--2024 academic year. 

In 2019, I won the [Waller Education Award](https://www.amstat.org/ASA/Your-Career/Awards/Waller-Awards.aspx) from the Section on Statistics and Data Science Education of the American Statistical Association and the [Outstanding Undergraduate Teaching Award](https://community.amstat.org/bostonchapter/awards/teachingaward) from the Boston Chapter of the ASA. I was a Mary P. Dolciani [Project NExT](http://archives.math.utk.edu/projnext/) Fellow for 2012--2013.

## Teaching history

```{r, include=FALSE}
library(dplyr)
library(tidyr)
teaching <- tibble::tribble(
  ~year, ~semester, ~course, ~course_short, ~url,
  2024, "Spring", "(on sabbatical)", "", NA,
  2023, "Fall", "(on sabbatical)", "", NA,
  2023, "Spring", "Data Journalism", "SDS 236", NA,
  2022, "Fall", "Reproducible Computing with Data", "SDS 100", "https://smithcollege-sds.github.io/sds100",
  2022, "Fall", "Introduction to Probability and Statistics", "SDS 220", NA,
  2022, "Spring", "Advanced Programming for Data Science", "SDS 270", NA,
  2022, "Spring", "Statistical & Data Sciences Capstone", "SDS 410", NA,
  2021, "Fall", "Statistical & Data Sciences Capstone", "SDS 410", NA,
  2021, "Spring", "Introduction to Data Science", "SDS 192", NA,
  2020, "Fall", "Introduction to Data Science", "SDS 192", NA,
  2020, "Spring", "Data Journalism", "SDS 236", NA,
  2020, "Spring", "Introduction to Data Science", "SDS 192", NA,
  2019, "Fall", "Topics in SDS: Programming for Data Science", "SDS 390", NA,
  2019, "Fall", "Statistical & Data Sciences Capstone", "SDS 410", NA,
  2019, "Spring", "Introduction to Data Science", "SDS 192", NA,
  2019, "Spring", "Statistical & Data Sciences Capstone", "SDS 410", NA,
  2018, "Spring", "Introduction to Data Science", "SDS 192",  "http://catalog.smith.edu//detail.php?term=201703&crn=41556",
  2018, "Spring", "Statistical & Data Sciences Capstone", "SDS 410", NA,
  2018, "Fall", "(on sabbatical)", "", NA,
  2017, "Fall", "Introduction to Data Science", "SDS 192", "http://catalog.smith.edu//detail.php?term=201801&crn=10672",
  2017, "Spring", "Introduction to Data Science", "SDS 192", "http://catalog.smith.edu//detail.php?term=201703&crn=41556",
  2016, "Spring", "Introduction to Data Science", "SDS 192", "http://catalog.smith.edu//detail.php?term=201603&crn=41556",
  2016, "Fall", "Introduction to Probability and Statistics", "MTH/SDS 220", "http://catalog.smith.edu//detail.php?term=201701&crn=20902",
  2015, "Spring", "Introduction to Probability and Statistics", "MTH 220", "http://catalog.smith.edu//detail.php?term=201503&crn=40598",
  2015, "Spring", "Multiple Regression", "MTH 291", "http://catalog.smith.edu//detail.php?term=201503&crn=40560",
  2015, "Fall", "Introduction to Probability and Statistics", "MTH/SDS 220", "http://catalog.smith.edu//detail.php?term=201601&crn=20902", 
  2014, "Spring", "Introduction to Probability and Statistics", "MTH 220", "http://catalog.smith.edu//detail.php?term=201403&crn=40598", 
  2014, "Fall", "Introduction to Probability and Statistics", "MTH 220", "http://catalog.smith.edu//detail.php?term=201501&crn=20218", 
  2014, "Fall", "Data Science", "MTH 292", "http://catalog.smith.edu//detail.php?term=201501&crn=20053",
  2013, "Spring", "Introduction to Discrete Mathematics", "MTH 153", "http://catalog.smith.edu/detail.php?term=201303&crn=30589", 
  2013, "Spring", "Probability & Statistics", "MTH 241", "http://catalog.smith.edu/detail.php?term=201303&crn=40049", 
  2013, "Fall", "Introduction to Discrete Mathematics", "MTH 153", "http://catalog.smith.edu//detail.php?term=201401&crn=10838", 
  2013, "Fall", "Data Science", "MTH 292", "http://catalog.smith.edu//detail.php?term=201401&crn=20053",
  2012, "Spring", "(dissertation)", "", NA,
  2012, "Fall", "Statistics: Introduction to Regression Analysis", "MTH 247", "http://catalog.smith.edu/detail.php?term=201301&crn=19319",
  2011, "Spring", "(dissertation)", "", NA,
  2011, "Fall", "(dissertation)", "", NA,
  2010, "Spring", "(dissertation)", "", NA, 
  2010, "Fall", "Combinatorics [Queens College]", "MATH636", "http://people.qc.cuny.edu/faculty/christopher.hanusa/courses/636fa10/Pages/default.aspx",
  2009, "Spring", "Elementary Probability and Statistics [Hunter College]", "STAT113", "http://math.hunter.cuny.edu/courses.shtml", 
  2009, "Fall", "Elementary Probability and Statistics [Hunter College]", "STAT113", "http://math.hunter.cuny.edu/courses.shtml", 
  2008, "Fall", "Elementary Probability and Statistics [Hunter College]", "STAT113", "http://math.hunter.cuny.edu/courses.shtml", 
) %>%
  mutate(
    html = ifelse(!is.na(url), 
                  paste0(course, " ([", course_short, "](", url , "))"), 
                  course)
  )
```

Over the past `r summarize(teaching, n_distinct(year))` years, I've taught `r nrow(teaching)` sections of `r summarize(teaching, n_distinct(course))` different courses over `r summarize(teaching, n_distinct(year, semester))` semesters. 

```{r, include=FALSE, eval=FALSE}
teaching %>%
  group_by(course_short) %>%
  count() %>%
  arrange(desc(n))
```


```{r teaching-record, echo=FALSE, message=FALSE}
teaching %>%
  select(year, semester, html) %>%
  group_by(Year = year, semester) %>%
  summarize(html = paste(html, collapse = "</br>")) %>%
  spread(key = semester, value = html) %>%
  arrange(desc(Year)) %>%
  select(Year, Spring, Fall) %>%
#  DT::datatable()
  knitr::kable()
```
