---
title: "Teaching"
---

My office hours for fall 2026 are:

- Tuesdays and Wednesdays from 2:45 pm -- 3:30 pm ET in McConnell 213
- Fridays from 10:00 am -- 11:30 am ET in McConnell 213
- by appointment

I was on sabbatical for the 2023--2024 academic year, and I spent the year at [Universidad EAFIT](https://www.eafit.edu.co/) in Medellín, Colombia. 

In 2019, I won the [Waller Education Award](https://www.amstat.org/ASA/Your-Career/Awards/Waller-Awards.aspx) from the Section on Statistics and Data Science Education of the American Statistical Association and the [Outstanding Undergraduate Teaching Award](https://community.amstat.org/bostonchapter/awards/teachingaward) from the Boston Chapter of the ASA. 
I was a Mary P. Dolciani [Project NExT](http://archives.math.utk.edu/projnext/) Fellow for 2012--2013.

## Teaching history

```{r, include=FALSE}
library(tidyverse)
teaching <- read_csv("teaching_record.csv") |>
  mutate(
    html = ifelse(!is.na(url), 
                  paste0(course, " ([", course_short, "](", url , "))"), 
                  course)
  )
```

Over the past `r summarize(teaching, n_distinct(year))` years, I've taught `r nrow(teaching)` sections of `r summarize(teaching, n_distinct(course))` different courses over `r summarize(teaching, n_distinct(year, semester))` semesters. 

```{r, include=FALSE, eval=FALSE}
teaching |>
  group_by(course_short) |>
  count() |>
  arrange(desc(n))
```


```{r teaching-record, echo=FALSE, message=FALSE}
teaching |>
  select(year, semester, html) |>
  group_by(Year = year, semester) |>
  summarize(html = paste(html, collapse = "</br>")) |>
  pivot_wider(names_from = semester, values_from = html) |>
  arrange(desc(Year)) |>
  select(Year, Spring, Fall) |>
#  DT::datatable()
  knitr::kable()
```
